Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-12 paper.tex
Fari fixes

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction}
We took the idea from our SPIRE paper and we made it great, using ZSTD compression and other tricks to improve the time complexity of the queries for the \ctr. Regarding \acumm, it was not possible to improve its speed (as it was already a few memory accesses per query), but we managed to compress it without increasing time complexity. We rock.

@@

@@

\subsection{Our model for compact trip representation}
In our previous structures proposed in \cite{brisaboa2018new}, we propose a work-in-progress model to represent the demand information for a public transportation network, as seen in the Figure~\ref{fig:er}.

@@

\section{Relevant queries}
\label{seq:rq}
In the context of public transportation networks, we are interested in solving two kinds of queries:

\begin{enumerate}[A)]
    \item Aggregation of passengers, asking for the gross number of users that boarded or alighted within an area and a time window. Furthermore, it can be also interesting to obtain the average load of a bus or a train between any two stops from its line.
    \item Movement patterns, or queries that focus on the sequence of trip stages. Examples of such queries are the number of times a stop was used to switch lines or the number of trips that started on a stop with another specific stop as the final destination.
\end{enumerate}

@@

As of today, we are not aware of any indexing structure that would allow to efficiently represent trajectories that could also support all the kinds of queries described in Section~\ref{seq:rq}. For this reason, we propose two data structures, \acumm~and~\ctr. The first is targeted for queries of type A, solving most aggregation queries in constant time, while the later can be used for queries of type B.

@@

@@

We use three complementary structures to represent each component of the sequence, as shown in Figure~\ref{fig:example_ctr}:
\begin{enumerate}[(i)]
    \item An adapted Compressed Suffix Array (CSA) over the stop identifiers of all trips, concatenated into a string with additional terminator symbols $\$$ appended at the end of each trip. While in the final CSA we assign these $\$$ a lexicographical value of 0 (thus smaller than any stop identifier), we assign them different values during the construction of the suffix array (A) to ensure that the entries for $\$$ in A maintain the same order as in the original text. Finally, we make a modification on $\Psi$ to make the entries of each $\$$ point to the start of its own trip instead of the next one. These two modifications are proven necessary for our implemented queries, at the expense of losing some of the properties of a classic CSA.
    \item Aligned to the entries of (i) there is a Wavelet Matrix (WM) for the line identifiers of each stop. Aligned to the $\$$ section we duplicate the starting lines of each trip. As a trivial optimization, we build a separate WM for every stop, allowing us to save space due to the fact that a single stop does not usually belong to many lines, thus the average height of these WM is no larger (and usually smaller) than the height of a single WM.
    \item A WM of jcodes aligned to the leaves of (ii). Note that this makes this structure dependant on (ii), which is coherent with the fact that journey codes themselves are relative to the line identifier. In case (ii) implements the optimization described, the entries of the WM must also be rearranged to match the delimited stops.
\end{enumerate}

>>>>

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%
\section{Introduction: sin hacer (queda para el final)}
We took the idea from our SPIRE paper and we made it great, using ZSTD compression and other tricks to improve the time complexity of the queries for the \ctr. Regarding \acumm, it was not possible to improve its speed (as it was already a few memory accesses per query), but we managed to compress it without increasing time complexity. We rock.

@@

Aqui no estaria mal, ademas de motivar ;) completar con la estructura del paper, y de paso decir que es lo nuevo VS lo de SPIRE. (ej. Esta es una version extendida del X, donde hemos tratado de solucionar nuevas operaciones como x..., viendo que algunas de ellas se volvían ineficientes en el CTR original, decidimos realizar una nueva variante (\ctr), que permite responder más consultas eficientemente. Así, en la Seccion 2 T-R, en la seccon 3 - MODELO , en la seccion 4 mostramos nuestras propuestas y cómo utilizarlas para resolver consutlas... etc etc)

@@

\section{Our model for compact trip representation}
In our previous structures proposed in \cite{brisaboa2018new}, we propose a work-in-progress model to represent the demand information for a public transportation network, as seen in the Figure~\ref{fig:er}.

@@

\subsection{Relevant queries}
\label{seq:rq}
In the context of public transportation networks, we are interested in solving two kinds of queries:

\begin{enumerate}[A)]
    \item Aggregation of passengers, asking for the gross number of users that boarded or alighted within an area and a time window. Furthermore, it can be also interesting to obtain the average load of a bus or a train between any two stops from its line.\marginpar{\tiny meteremos algún ejemplo de las consultas que después implementaremos}
    \item Movement patterns, or queries that focus on the sequence of trip stages. Examples of such queries are the number of times a stop was used to switch lines or the number of trips that started on a stop with another specific stop as the final destination. 
\end{enumerate}

En concreto, en este paper nos hemos centrado en ...
\begin{itemize}
    \item  consulta 1
    \item consutla 2

\end{itemize}

@@

As of today, we are not aware of any indexing structure that would allow to efficiently represent trajectories that could also support all the kinds of queries described in Section~\ref{seq:rq}. For this reason, we propose two data structures, \acumm~and~\ctr. The former is targeted for queries of type A, solving most aggregation queries in constant time, while the later can be used for queries of type B.

@@

\subsection{CTR version de spire...}
y despues la variante nueva (CTR2M).

@@

We use three complementary structures to represent each component of the sequence, as shown in Figure~\ref{fig:example_ctr}:
\begin{enumerate}[(i)]
    \item An adapted Compressed Suffix Array (CSA) over the stop identifiers of all trips, concatenated into a string with additional terminator symbols $\$$ appended at the end of each trip. While in the final CSA we assign these $\$$ a lexicographical value of 0 (thus smaller than any stop identifier), we assign them different values during the construction of the suffix array (A) to ensure that the entries for $\$$ in A maintain the same order as in the original text. Finally, we make a modification on $\Psi$ to make the entries of each $\$$ point to the start of its own trip instead of the next one. These two modifications are proven necessary for our implemented queries, at the expense of losing some of the properties of a classic CSA.
    \item WML: Aligned to the entries of (i) there is a Wavelet Matrix (WM) for the line identifiers of each stop. Aligned to the $\$$ section we duplicate the starting lines of each trip. As a trivial optimization, we build a separate WM for every stop, allowing us to save space due to the fact that a single stop does not usually belong to many lines, thus the average height of these WM is no larger (and usually smaller) than the height of a single WM.
    \item WVJ: A WM of jcodes aligned to the leaves of (ii). Note that this makes this structure dependant on (ii), which is coherent with the fact that journey codes themselves are relative to the line identifier. In case (ii) implements the optimization described, the entries of the WM must also be rearranged to match the delimited stops.
\end{enumerate}
